---
title: "Cofit x Genensis 醫療大數據 (分析報告)"
author: "By BigData Team"
date: "Last Updated On `r Sys.Date()`"
knit: "bookdown::render_book"
site: bookdown::bookdown_site
documentclass: book
output:
  bookdown::gitbook:
    dev: svglite
    css: css/style.css
    includes:
      in_header: GA_script.html
      after_body: string_rm.html
    split_by: section
    number_sections: true
    toc_depth: 3
    self_contained: false
    config:
      toc:
        collapse: subsection
      download: null
      edit: null
      sharing: null
      search: yes
  bookdown::html_chapters:
    css: [css/style.css, css/toc.css]
  bookdown::pdf_book:
    pandoc_args: --top-level-division=chapter
    toc_depth: 3
    toc_unnumbered: no
    toc_appendix: yes
    quote_footer: ["\\VA{", "}{}"]
  bookdown::epub_book:
    dev: svglite
    stylesheet: css/style.css
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
library(googleVis)
knitr::opts_chunk$set(echo = FALSE, comment = NA, results = 'asis', warning = FALSE, error = FALSE, message = FALSE, fig.align = 'center')
options(knitr.graphics.auto_pdf = TRUE, gvis.plot.tag = 'chart')
```

```{r input df from PostgreSQL, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# source("~/Lincoln/02.Work/04. R&D/02. HIIS_OPP/00.Gitbook/01.CG/CG_report/rscript/lin_function.R")

# #Does source() rscript need to move to the same project dir??
  # lin_connect_db("connect")
  # path_sql <- "~/Lincoln/02.Work/04. R&D/02. HIIS_OPP/00.Gitbook/01.CG/CG_report/sql/"

  # tmp_01 <- DBI::dbGetQuery(db, readr::read_file(paste0(path_sql, "01_profile.sql")))
  # tmp_02 <- DBI::dbGetQuery(db, readr::read_file(paste0(path_sql, "02_inbody.sql")))
  # tmp_03 <- DBI::dbGetQuery(db, readr::read_file(paste0(path_sql, "03_FLC_self_report.sql")))
  # tmp_04 <- DBI::dbGetQuery(db, readr::read_file(paste0(path_sql, "04_non_FLC_self_report.sql")))
  # tmp_05 <- DBI::dbGetQuery(db, readr::read_file(paste0(path_sql, "05_biochem.sql")))
  # 
  # tmp_06 <- DBI::dbGetQuery(db, readr::read_file(paste0(path_sql, "06_Diet_day.sql")))
  # tmp_07 <- DBI::dbGetQuery(db, readr::read_file(paste0(path_sql, "07_Diet_meal.sql")))
  # tmp_08 <- DBI::dbGetQuery(db, readr::read_file(paste0(path_sql, "08_3D_scanner.sql")))
  # tmp_09 <- DBI::dbGetQuery(db, readr::read_file(paste0(path_sql, "09_hormone.sql")))

  # lin_connect_db("exit")
  # rm(path_sql)
  # 
  
```

```{r input rscript, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# source("~/Lincoln/02.Work/04. R&D/02. HIIS_OPP/00.Gitbook/01.CG/CG_report/rscript/lin_function.R")
#  source("~/Lincoln/02.Work/04. R&D/02. HIIS_OPP/00.Gitbook/01.CG/CG_report/rscript/00-read_clinic_list.R")
# source("~/Lincoln/02.Work/04. R&D/02. HIIS_OPP/00.Gitbook/01.CG/CG_report/rscript/00-data_preprocessing.R")
# source("~/Lincoln/02.Work/04. R&D/02. HIIS_OPP/00.Gitbook/01.CG/CG_report/rscript/01.1-venns.R")
# source("~/Lincoln/02.Work/04. R&D/02. HIIS_OPP/00.Gitbook/01.CG/CG_report/rscript/01.2-global_treatment.R")
# source("~/Lincoln/02.Work/04. R&D/02. HIIS_OPP/00.Gitbook/01.CG/CG_report/rscript/01.3-testosterone_effectiveness.R")
# 
#  source("~/Lincoln/02.Work/04. R&D/02. HIIS_OPP/00.Gitbook/01.CG/CG_report/rscript/00-main_page_stat.R")

```

```{r alternative try I: input workspace, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}

load("~/Lincoln/02.Work/04. R&D/02. HIIS_OPP/00.Gitbook/01.CG/WSpace_preproc.RData")


#Load packages
source("~/Lincoln/02.Work/04. R&D/02. HIIS_OPP/00.Gitbook/01.CG/CG_report/rscript/lin_function.R")

library(pacman)
pacman::p_load(magrittr, knitr, kableExtra, dplyr, readr, readxl, tibble, showtext, extraInserts,
               ggvenn, ggplot2,knitr, kableExtra, openxlsx, lubridate, cowplot, ggpubr, webshot,
               stringr)
#font
font_add(family = "berlin_default", regular = "~/Lincoln/02.Work/04. R&D/02. HIIS_OPP/00.Gitbook/01.CG/CG_report/data/font/STHeiti Light.ttc")
showtext_auto(enable = TRUE)

source("~/Lincoln/02.Work/04. R&D/02. HIIS_OPP/00.Gitbook/01.CG/CG_report/rscript/00-main_page_stat.R")



```

# Highlight {#index .unnumbered}

**1.初日體系診所(秀傳、初日、小宙)累積客戶統計：**

```{r, results='asis', fig.width = 6}
client_monthly_stat_report %>% plot()
```

**#＃總計「累積服務客戶數」:** [**`r client_monthly_stat_report_total_client`**]{.underline}**(人次)**

**2.初日減重門診 - 單次療程**(分析人數: `r success_df_freq[["Total"]] %>% max()`)：

-   [**成功減重人數(%)**]{.underline}，總計`r success_df_freq[success_df_freq$gender == "Total", "success"]`人(成功率:[**`r success_df_pct[success_df_freq$gender == "Total", "success"]`**]{.underline})。
-   [**女性:**]{.underline}`r success_df_freq[success_df_freq$gender == "female", "success"]`人(成功率:[**`r success_df_pct[success_df_freq$gender == "female", "success"]`**]{.underline})。
-   [**男性:**]{.underline}`r success_df_freq[success_df_freq$gender == "male", "success"]`人(成功率:[**`r success_df_pct[success_df_freq$gender == "male", "success"]`**]{.underline})。

```{r, results='asis', fig.width = 4, fig.height= 4}
plot_stack_col_female %>% plot()
```

```{r, results='asis', fig.width = 4, fig.height= 4}
plot_stack_col_male %>% plot()
```

<!-- Introduction context...(editing) -->

<!-- #### Disclaimer {.unnumbered} -->

<!-- The information in this report is provided ...(editing). -->

[(識別碼：`r lin_timestamp()`)]{style="float:right"}
